Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\subsubsection{Cross Attention}
The key factor in target speaker extraction is to inject the information of target speaker 
into the mixture. SEF-Net \cite{sef_net} has proposed an embedding free way to inject the 
target speaker information into the mixture by using cross attention module. This approach 
has

>>>>

\subsubsection{Cross Attention}
The key factor in target speaker extraction is to inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module.
